---
title: "pstat131 hw1"
author: "Shefali Singh"
date: "4/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

Machine Learning Main Ideas
1. Supervised learning is when there is a response yi associated with every observation (predictor variables). A model is fit in a way that will predict the response or help to better understand the relationship between the predictors and response. Unsupervised learning is when there is no response yi for every observation, and in this case, unlike with supervised learning, a linear regression model cannot be fit. However, cluster analysis can be used instead.

2. A regression model has a quantitative response, while a classification model has a qualitative response. Logistic regression is classification method, but can be thought of as regression as well because it estimates class probabilities (categories of qualititative variables). (textbook page 28)

3. Two commonly used metrics for regression ML problems include mean square error and root mean square error, while classification uses accuracy and log-loss.

4. Descriptive models: mostly use unsupervised learning to describe and classify past observations; Inferential models: compares the models to the data; predictive models: predicts future outcomes based on previous data

5. mechanistic: ; empirically driven: 

6. Given a voter's profile and looking for which way they will vote in the future is predictive as it uses past data to determine the most likely future outcome. Personal contact would be inferential as there is not previous data about the situation and the voter.


Exploratory Data Analysis:
1. histogram of hwy model 
```{r}
# View(mpg)
hist(mpg$hwy)
```
The data do not seem normally distributed. The highest frequency is from 25-30 mpg, with 15-20 coming second.

2. 
```{r}
plot(mpg$hwy, mpg$cty)
```
There seems to be a positive linear relationship between cty and mpg, which means as one increases, so does the other.

3. bar plot of manufacturer
```{r}
m <- table(mpg$manufacturer)
barplot(m)
barplot(m, horiz=TRUE)
```
Dodge produced the most while Lincoln produced the least.

4. 
```{r}
boxplot(mpg$hwy ~ mpg$cyl)
```
It seems as if hwy decreases with an increase in cyl.

5. 
```{r}
# install.packages("corrplot")
library(corrplot)
# corrplot(mpg, order = 'FPC', type = 'lower', diag = FALSE)
```

